Examining the Frequency of 'E': A Quantitative Analysis of Pride and Prejudice

### 2024-03-13 outputs/paper/paper.qmd
Update paper.qmd

---
title: "Letters used in Pride and Prejudice"
author: 
  - Sindhu Priya Mallavarapu
  - Jena Shah
thanks: "Code and data are available at: https://github.com/MSindhuPriya/letters_jane_austen "
date: today
date-format: long
abstract: "This paper explores the distribution of the letter 'e' in Jane Austen's Pride and Prejudice to understand if its frequency of occurrence correlates with the amount of words in the text. The methodology involves counting the occurrences of the letter 'e' in the first ten lines of each chapter gathered from the dataset obtained from Project Gutenberg. We found that the frequency of the letter “e” increases as the amount of words in the text increases. This analysis can be of interest to linguists as it can help them to identify patterns and characteristics of the English language, better understand the writing style of Jane Austen, and understand the evolution of the English language over time."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Examining the Frequency of 'E': A Quantitative Analysis of Pride and Prejudice"
author: 
  - Sindhu Priya Mallavarapu
  - Jena Shah
thanks: "Code and data are available at: https://github.com/MSindhuPriya/letters_jane_austen "
date: today
date-format: long
abstract: "This paper explores the distribution of the letter 'e' in Jane Austen's Pride and Prejudice to understand if its frequency of occurrence correlates with the amount of words in the text. The methodology involves counting the occurrences of the letter 'e' in the first ten lines of each chapter gathered from the dataset obtained from Project Gutenberg. We found that the frequency of the letter “e” increases as the amount of words in the text increases. This analysis can be of interest to linguists as it can help them to identify patterns and characteristics of the English language, better understand the writing style of Jane Austen, and understand the evolution of the English language over time."
format: pdf
number-sections: true
bibliography: references.bib
---
